Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-12 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
updates supp

\caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot), projected at the SHMS collimator.
  The projection at the SHMS collimator clearly shows that the acceptance of the SHMS is driven by that of the HMS.}

@@

@@

\indent Figure \ref{fig:data_coll_cuts} (left) shows

@@

\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$.
The data has been normalized by the total charge and corrected for the inefficiencies described in the Letter. Radiative and bin-centering corrections have not been applied for these plots.
The same event selection cuts mentioned in the previous sections were applied (including the $Q^{2}$ cut), with the exception of the $Q^{2}$ distribution itself.
Only the first dataset (out of 2) for the 580 and (out of 3) for the 750 MeV/c settings are shown. 

@@

\includegraphics[scale=0.25]{plots/d2_kin_thnq35.png}
\caption{Deuteron kinematic distributions for the 80 (blue), 580 (set1, red) and 750 (set1, magenta) MeV/c cental missing momentum settings at $\theta_{nq}=35^{\circ}$.}

@@

\includegraphics[scale=0.25]{plots/d2_kin_thnq45.png}

@@

\includegraphics[scale=0.3]{plots/tgt_bkg_d2_pm580_allthnq.png}

@@

\includegraphics[scale=0.30]{plots/RC_factor.png}

@@

\includegraphics[scale=0.30]{plots/BC_factor.png}

>>>>

\caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot),
  projected at the SHMS collimator.}

@@

\indent Figure \ref{fig:data_coll_cuts} (left) shows a geometrical (red octogon) cut on the reconstructed events projected at the HMS collimator to ensure
that all events that enter the spectrometer pass through the collimator, and not re-scatter at the edges. This cut is needed since protons that enter the
HMS can punch through the collimator with a probability that is related to the proton-Aluminum total cross section. Figure \ref{fig:data_coll_cuts} (right)
shows the correlated events projected at the SHMS collimator which clearly shows that the events are well within the collimator which indicates that the SHMS
acceptance is driven by that of the HMS. Figure \ref{fig:simc_coll_cuts} shows the same acceptance cuts as previously described, but for simulation.\\

@@

@@

\noindent Figures \ref{fig:d2_kin_35deg} and \ref{fig:d2_kin_45deg} show the fundamental kinematic variable distributions for each of the
central missing momentum settings at $\theta_{nq}=35^{\circ}$ and $45^{\circ}$. The data has been normalized by the total charge and corrected
for the inefficiencies described in the Letter. The same event selection cuts mentioned in the previous section were applied. 

@@

\includegraphics[scale=0.18]{plots/d2_kin_thnq35.png}
\caption{Deuteron kinematic distributions for the 80 (blue), 580 (red) and 750 (magenta) MeV/c setting at $\theta_{nq}=35^{\circ}$.}

@@

\includegraphics[scale=0.18]{plots/d2_kin_thnq45.png}

@@

\includegraphics[scale=0.33]{plots/tgt_bkg_d2_pm580_allthnq.png}

@@

\includegraphics[scale=0.27]{plots/RC_factor.png}

@@

\includegraphics[scale=0.27]{plots/BC_factor.png}
